Effectful Semantics for Substructural SSA

### 2023-11-05 pldi24/paper.tex
Tap at distributivity structure

\begin{definition}[Distributive category] 
  A \textbf{distributive category} is a premonoidal category with coproducts equipped with a natural family of central isomorphisms \(\delta_{A, B, C}: (A + B) \otimes C \simeq A \otimes C + B \otimes C\).
\end{definition}

\TODO{results on distributivity of monads}

>>>>

\subsection{Distributivity}

\begin{definition}[If-then-else category] \
  \TODO{this}
\end{definition}

\TODO{results on if-then-else of monads}

\begin{definition}[Distributive (pre)monoidal category] 
  A \textbf{distributive (pre)monoidal category} is a (pre)monoidal category with all finite coproducts equipped with a natural family of central isomorphisms \(\delta_{A, B, C}: (A + B) \otimes C \simeq A \otimes C + B \otimes C\).
  \TODO{complex coherence conditions in \cite{laplaza-distributivity}, what we need for if-then-else}
\end{definition}
